\textbf{Pinnacle} \rdate{2017-} \newline
\textit{Skills Used: iOS Development, Swift, Core Data, Concurrent Programming, Testing}
%
\begin{itemize}[leftmargin=0mm]
\item An iOS client for the Pinboard bookmarking service under active
  development. It provides a powerful interface for users to read and organise
  their collection of bookmarks on iPhone and iPad.
\item I split the sync, networking and model code into separate frameworks to
  ensure that separation of concerns is achieved and to increase code
  reuse. This also made the code highly testable and I have written a full suite
  of unit tests for these layers.
\item I adopted the coordinator pattern for the application's architecture which
  reduces the complexity of view controllers, improves their testability and
  augments the standard design patterns of UIKit rather than working against
  them.
\item I implemented persistence using Core Data and spent significant time in
  instruments profiling the memory usage and timing of the app's sync code. I
  have implemented a sync system that can import tens of thousands of bookmarks
  from JSON data within reasonable time and memory constraints. I have written a
  set of automated performance tests to monitor for any regressions.
\item All networking and persistence is concurrent to maintain a smooth user
  experience throughout the app. Initially I designed the networking and
  persistence APIs to use completion handlers to manage asynchrony. However,
  maintenance became a nightmare and I refactored the APIs to use promises. Now
  I can't wait for native async/await in Swift.
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../vita"
%%% End:
