\mhead{Experience}%
\textbf{Lead iOS Developer}, Apposing Ltd. \rdate{2018--}

Involved in the development of applications for clients through all phases of
the development process, from conception to release. I lead a small team of
developers and have worked on a variety of applications including retail,
financial and telematics apps. I have introduced new ideas and tools to the team
such as coordinators, promises and a networking library that has been developed
into an open-source project.

\medskip

\textit{Interesting Challenges:}

\smallskip

\begin{itemize}
\item Took over development of a retail app for a major UK clothing retailer on
  a tight schedule. I worked closely with external API developers and product
  owners while effectively distributing work throughout our team to complete the
  project on time. Post-release, I worked with an external development team to
  integrate an exciting user experience into the app for a major global fashion
  brand.

\item Developed a driving telematics app for an insurance start-up that monitors
  a user's driving and suggests how they can improve. I built a telematics
  library using an Elm inspired architecture to model tracking state and
  side-effects while modelling external hardware sensors as RxSwift
  observables. The architecture bought compile time checks around the possible
  states of the tracking library and made it easy to incorporate real-world data
  into unit tests.

\item Worked closely with designers to build a stunning investment app for a
  fintech startup. A key challenge in the development of the app was a
  multi-step onboarding flow that users could leave and return to at any
  point. I used coordinators to break the flow into isolated sub-flows that the
  app could then launch directly into based on the user's progress.

\end{itemize}

\bigskip

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../vita"
%%% End:
