\textbf{Lead iOS Developer}, Apposing Ltd. \rdate{January 2018--August 2019}\\
\textit{Skills Used: Swift, Objective-C, git, Testing, RxSwift}

Developed apps for clients, working closely with them through all phases of the
development process. I led a small team of developers and worked on a variety of
applications including retail, financial and telematics apps. I introduced new
ideas and tools to the team such as coordinators, promises and a networking
library that has been developed into an open-source project.

% \medskip
\newpage % LAYOUTHACK

\textit{Interesting Challenges at Apposing:}

\smallskip

\begin{itemize}
\item Took over development of a retail app for a large UK clothing retailer on
  a tight schedule. I worked closely with external API developers and product
  owners while effectively distributing work throughout the team to complete the
  project on time. Post-release, I worked with an external development team and
  a major global fashion brand to integrate an exciting user experience into the
  app.

\item Developed a driving telematics app for an insurance start-up that monitors
  a user's driving and suggests how they can improve. I built a telematics
  library using an Elm inspired architecture to model tracking state and
  side-effects. The architecture bought compile time checks around the possible
  states of the tracking library and made it easy to incorporate real-world data
  into automated tests.

\item Worked closely with designers to build a beautiful investment app for a
  fintech startup. A key challenge in the development of the app was a
  multi-step onboarding flow that users could leave and return to at any
  point. I used coordinators to break the flow into isolated sub-flows that the
  app could then launch directly into based on the user's progress.

\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../vita"
%%% End:
